Evaluating Variable Importances

### 2019-07-23 Scripts/evaluating_variable_importances.Rmd
updated with preprocessed tads

```{r}
#GM12878
all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_5kb$Feature,
                                        varimp_gm12878_5kb$aveimp5kb,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_tfbs) <- c("Feature", "ave10kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
all_varimps_gm12878_tfbs <- melt(all_varimps_gm12878_tfbs)

>>>>

```{r}
#GM12878
all_varimps_gm12878_tfbs <- cbind.data.frame(varimp_gm12878_5kb$Feature,
                                        varimp_gm12878_5kb$aveimp5kb,
                                        varimp_gm12878_10kb$aveimp10kb,
                                        varimp_gm12878_25kb$aveimp25kb,
                                        varimp_gm12878_50kb$aveimp50kb,
                                        varimp_gm12878_100kb$aveimp100kb)
names(all_varimps_gm12878_tfbs) <- c("Feature", "ave5kb", "ave10kb", "ave25kb", "ave50kb", "ave100kb")
all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[order(rowMeans(all_varimps_gm12878_tfbs[,-1]), decreasing = TRUE),]
#all_varimps_gm12878_tfbs <- all_varimps_gm12878_tfbs[1:20,]
all_varimps_gm12878_tfbs <- melt(all_varimps_gm12878_tfbs)
